Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-30 writeup/gz_hubble_data.tex
Slight caveat on slope limit. Minor comment 2; closes #203.

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modelled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
\emph{not} a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest. We quantify this by measuring the slope of the best-fit
polynomial to the vote fractions; regions of the bins with a slope less than 0.4 are considered
\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
\ffeaturesrest{} value.  Galaxies in this region are referred to as the
\emph{lower limit} sample, because the most stringent correction available is
that the weighted \ffeatures{} is a lower limit to the true value.  These
regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncoloured (white)
regions of the plot have sufficiently high slopes to consider the relationship
as single-valued; galaxies in these regions are considered ``correctable'', and
only these are used in measuring the parameters for the $\zeta$ function
(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
5~galaxies were considered; regions with fewer than 5~galaxies are considered
to have ``not enough information'' to determine the \ffeaturesz{} and
\ffeaturesrest{} relationship, coloured grey in Figure~\ref{fig:f_vs_f}. These
galaxies are hereafter referred to as the ``NEI'' sample.

>>>>

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modelled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
\emph{not} a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest. We quantify this by measuring the slope of the best-fit
polynomial to the vote fractions. Regions within the bins with a slope less than 0.4
(a boundary selected through manual inspection and testing) are considered
\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
\ffeaturesrest{} value.  Galaxies in this region are referred to as the
\emph{lower limit} sample, because the most stringent correction available is
that the weighted \ffeatures{} is a lower limit to the true value.  These
regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncoloured (white)
regions of the plot have sufficiently high slopes to consider the relationship
as single-valued; galaxies in these regions are considered ``correctable'', and
only these are used in measuring the parameters for the $\zeta$ function
(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
5~galaxies were considered; regions with fewer than 5~galaxies are considered
to have ``not enough information'' to determine the \ffeaturesz{} and
\ffeaturesrest{} relationship, coloured grey in Figure~\ref{fig:f_vs_f}. These
galaxies are hereafter referred to as the ``NEI'' sample.
